FictionEro - Data Cleaning

### 2024-03-25 analysis/1_cleaning.qmd
update

@@

outliers <- c(
  # "S206"  # Collapsed RTs in both phases
  # "S399"  # Negative Arousal-Valence correlations
  "S428",  # Only 0s for arousal (creates statistical problems)
  "S498",  # Only 0s for arousal (creates statistical problems)
  "S508"  # Only 0s for arousal (creates statistical problems)
  )
potentials <- list()
```

@@

#### 1-60

plot_hist(dftask[dftask$Participant %in% df$Participant[1:60], ])
```

#### 61-120

plot_hist(dftask[dftask$Participant %in% df$Participant[61:120], ])
```

#### 121-180

plot_hist(dftask[dftask$Participant %in% df$Participant[121:180], ])
```

#### 181-240

plot_hist(dftask[dftask$Participant %in% df$Participant[181:240], ])
```

#### 241-300

plot_hist(dftask[dftask$Participant %in% df$Participant[241:264], ])
```

@@

```{r}
# dftask[dftask$Participant == "S428", "Arousal"]
# dftask[dftask$Participant == "S498", "Arousal"]
# dftask[dftask$Participant == "S508", "Arousal"]
dat <- dftask |> 
  filter(!Participant %in% c("S428", "S498", "S508")) |> 
  summarize(cor_ArVal = cor(Arousal, Valence),
            cor_ArEnt = cor(Arousal, Enticement),
            .by="Participant")

@@

```{r}
c(as.character(potentials$expe_duration$Participant), 
  as.character(potentials$emo_diff$Participant), 
  as.character(potentials$emo_cor$Participant)) |> 
  table()
```

@@

```{r}
df <- filter(df, !Participant %in% outliers)
dftask <- filter(dftask, Participant %in% df$Participant)
```

@@

@@

ega <- list()
for(model in c("glasso", "TMFG")) {
  for(algo in c("walktrap", "louvain")) {
    for(type in c("ega", "ega.fit", "riEGA")) {  # "hierega"
      if(type=="ega.fit" & algo=="louvain") next  # Too slow
      ega[[paste0(model, "_", algo, "_", type)]] <- EGAnet::bootEGA(
        data = bait,
        seed=123,
        model=model,
        algorithm=algo,
        EGA.type=type,
        type="resampling",
        plot.itemStability=FALSE,
        verbose=FALSE)
      }
   }
}

@@

ega_scores <-  EGAnet::net.scores(bait, ega_final)$scores$std.scores |> 
  as.data.frame() |> 
  setNames(c("EGA_Text", "EGA_Image", "EGA_Videos")) 
```

@@

df <- full_join(df, scores, by="Participant")
```

>>>>

#### Spanish

plot_recruitement(filter(df, Language == "Spanish"))
table_recruitment(filter(df, Language == "Spanish"))
```

@@

outliers <- c(
  # "S206"  # Collapsed RTs in both phases
  # "S399"  # Negative Arousal-Valence correlations
)
potentials <- list()
```

@@

<!-- ::: {.panel-tabset} -->

<!-- #### 1-60 -->

<!-- ```{r} -->
<!-- #| fig-width: 15 -->
<!-- #| fig-height: 15 -->
<!-- #| eval: false -->

<!-- plot_hist(dftask[dftask$Participant %in% df$Participant[1:60], ]) -->
<!-- ``` -->

<!-- #### 61-120 -->

<!-- ```{r} -->
<!-- #| fig-width: 15 -->
<!-- #| fig-height: 15 -->
<!-- #| eval: false -->

<!-- plot_hist(dftask[dftask$Participant %in% df$Participant[61:120], ]) -->
<!-- ``` -->

<!-- #### 121-180 -->

<!-- ```{r} -->
<!-- #| fig-width: 15 -->
<!-- #| fig-height: 15 -->
<!-- #| eval: false -->

<!-- plot_hist(dftask[dftask$Participant %in% df$Participant[121:180], ]) -->
<!-- ``` -->

<!-- #### 181-240 -->

<!-- ```{r} -->
<!-- #| fig-width: 15 -->
<!-- #| fig-height: 15 -->
<!-- #| eval: false -->

<!-- plot_hist(dftask[dftask$Participant %in% df$Participant[181:240], ]) -->
<!-- ``` -->

<!-- #### 241-300 -->

<!-- ```{r} -->
<!-- #| fig-width: 15 -->
<!-- #| fig-height: 15 -->
<!-- #| eval: false -->

<!-- plot_hist(dftask[dftask$Participant %in% df$Participant[241:264], ]) -->
<!-- ``` -->

<!-- ::: -->

@@

```{r}
# Single arousal response (0)
outliers <- summarize(dftask, n = length(unique(Arousal)), .by="Participant") |> 
  filter(n == 1) |> 
  select(Participant) |> 
  pull() |> 
  c(outliers)

dat <- dftask |> 
  filter(!Participant %in% outliers) |> 
  summarize(cor_ArVal = cor(Arousal, Valence),
            cor_ArEnt = cor(Arousal, Enticement),
            .by="Participant")

@@

We removed `r length(outliers)` that showed no variation in their arousal response.

```{r}
# c(as.character(potentials$expe_duration$Participant), 
#   as.character(potentials$emo_diff$Participant), 
#   as.character(potentials$emo_cor$Participant)) |> 
#   table()
#   
df <- filter(df, !Participant %in% outliers)
dftask <- filter(dftask, !Participant %in% outliers)
```

@@

```{r}
df <- filter(df, !Participant %in% outliers)
dftask <- filter(dftask, !Participant %in% outliers)
```

@@

### System

```{r p_demographics_settings}
df$Screen_Size <- sqrt(df$Screen_Width * df$Screen_Height)

df |> 
  ggplot(aes(x = Screen_Size)) +
  geom_histogram() +
  scale_y_continuous(expand = c(0, 0), breaks= scales::pretty_breaks()) +
  labs(x =  expression("Screen Size ("~sqrt(Number~of~Pixels)~")"), y = "Number of Participants", title = "Screen Size") +
  theme_modern(axis.title.space = 15) +
  theme(
    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
    axis.text.y = element_text(size = rel(1.1)),
    axis.text.x = element_text(size = rel(1.1))
  )
```

@@

ega <- list()
for(model in c("glasso", "TMFG")) {
  for(algo in c("walktrap", "louvain")) {
    for(type in c("ega", "ega.fit", "riEGA")) {  # "hierega"
      if(type=="ega.fit" & algo=="louvain") next  # Too slow
      ega[[paste0(model, "_", algo, "_", type)]] <- EGAnet::bootEGA(
        data = bait,
        seed=123,
        model=model,
        algorithm=algo,
        EGA.type=type,
        type="resampling",
        plot.typicalStructure=FALSE,
        verbose=FALSE)
      }
   }
}

@@

ega_scores <-  EGAnet::net.scores(bait, ega_final)$scores$std.scores |> 
  as.data.frame() |> 
  setNames(c("EGA_Image", "EGA_Videos", "EGA_Text")) 
```

@@

df <- merge(df, scores, by="Participant")
```
